Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-08-30 pnas/Towards.tex
Added results for TRPV1

@@

The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB)~\cite{pdb} as 1QLQ. We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$.

>>>>

\begin{figure*}
    \centering
    \includegraphics[angle=270, width=0.3\textwidth]{TRPV1_rec.eps}
    \caption{Reconstruction of the TRPV1 molecule from its clean first 3 autocorrelations. The reconstruction is shown in gray while the ground truth is shown in yellow.}
    \label{fig:TRPV1_recon}
\end{figure*}

@@

The true volume used in both experiments was the Bovine Pancreatic Trypsin Inhibitor (BPTI) mutant with altered binding loop sequence, whos atomic model is available in the Protein Data Bank (PDB)~\cite{pdb} as 1QLQ. We generated an EM map from this atomic model in UCSF Chimera~\cite{pettersen2004ucsf} at a resolution of 5 \AA, and cropped it to remove zeros at the boundary to obtain a volume of size $31^3$. We also present a reconstruction of TRPV1 in complex with DkTx and RTX, whose EM map is available in the  Electron Microscopy Data Bank (EMDB)~\cite{emdb} as EMD-8117. The original map has size $192^3$, and we downsample it to size $20^3$. To generate the ground truth for our reconstructions, we expanded both volumes as in \eqref{eq:volume_expansion_app} with cutoff $L = 5$. For the TRPV1 reconstruction, the optimizer converged to a point giving relative $\ell_2$ error of $10^{-6}$ in the first three autocorrelations and an error of $10^{-1}$ in the expansion coefficients of the volume. Similarly, \TODO{Fill details for BPTI}. This illustrates the ill-conditioning of the map between the volume and its first three autocorrelations that prevents us from obtaining results from noisy data.
